Meta-analysis of fungicide application timing for powdery mildew management

### 2020-02-12 04_Prep_data.Rmd
Updated with AUDPStairs

@@

# correct dates (this has been done in wrangle file but not updated yet in the data-set)
PM_MB_means[PM_MB_means$trial_ref == "mung1516/01", "harvest_date"] <- as.Date("2016-05-06", format = "%Y-%m-%d")
PM_MB_means[PM_MB_means$trial_ref == "mung1516/01", "final_assessment"] <- final_assessment = as.Date("2016-04-15", format = "%Y-%m-%d")

#curiouspw10-
```

>>>>

```{r Yield_vs_AUDPS}

slimmer_PM_dat %>%
   #filter(AUDPC_m <=280)%>%
#   filter(fungicide_ai == "control")%>%
   ggplot(aes(x = grain_yield.t.ha, y = AUDPS_m))+
   geom_point()

summary(lm(grain_yield.t.ha ~ AUDPS_m, data = slimmer_PM_dat, AUDPS_m <= 280))

plot(grain_yield.t.ha. ~ AUDPS_m,data = PM_MB_means)
abline(lm(grain_yield.t.ha. ~ AUDPS_m, data = PM_MB_means))

for(i in sm2lg$trial_ref){
   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i, ]
   if(any(is.na(dat1$grain_yield.t.ha.))){next}
   if(any(is.na(dat1$AUDPS_m))){next}

plot(grain_yield.t.ha. ~ AUDPS_m, 
     data = dat1, main = paste(dat1$location[1],(dat1$year[1])),
     ylim = c(0,max(PM_MB_means$grain_yield.t.ha., na.rm = TRUE)), 
     xlim = c(0,max(PM_MB_means$AUDPS_m, na.rm = TRUE)))
abline(lm(grain_yield.t.ha. ~ AUDPS_m, data = dat1))
points(grain_yield.t.ha. ~ AUDPS_m, data = dat1[dat1$fungicide_ai == "control",], col = "red")

@@
